Adopting agile in the large: motivations, success factors and challenges

### 2014-05-08 journal/article.tex
Future research ideas

>>>>

* Compare to change leadership research, and organizational research. Which
  challenges are typical to any organization, which are specific to software
  development organizations.

* Compare how recommendations in large scale application models of agile relate
  to the challenges and success factors reported in the transformaiton proecss.
